---
title             : "Combining ABM with rTMS"
shorttitle        : "Combining ABM with rTMS"

author: 
  - name          : "Leonore Bovy"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Kapittelweg 29,  6525 EN Nijmegen, The Netherlands. P.O. Box 9101 6500 HB Nijmegen The Netherlands"
    email         : "l.bovy@donders.ru.nl"

affiliation:
  - id            : "1"
    institution   : "Donders Institute"
  - id            : "2"
    institution   : "Radboudumc"

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "attentional bias modification, repetitive transcranial magnetic stimulation, depression, mood, dysphoria"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_word
---


```{r install_package, include = FALSE}
#make sure to comment out when running the code a second time
#devtools::install_github("crsh/papaja")
#devtools::install_github("doomlab/MOTE")
```

```{r load_packages, include = FALSE}
suppressWarnings(suppressMessages(library(Matrix)))
suppressWarnings(suppressMessages(library(pbkrtest)))
suppressWarnings(suppressMessages(library(lme4)))
suppressWarnings(suppressMessages(library(parallel)))
suppressWarnings(suppressMessages(library(afex)))
suppressWarnings(suppressMessages(library(boot)))
suppressWarnings(suppressMessages(library(effects)))
suppressWarnings(suppressMessages(library(car)))
suppressWarnings(suppressMessages(library(lattice)))
suppressWarnings(suppressMessages(library(psych)))
suppressWarnings(suppressMessages(library(pastecs)))
suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(Hmisc)))
suppressWarnings(suppressMessages(library(haven)))
suppressWarnings(suppressMessages(library(nlme)))
suppressWarnings(suppressMessages(library(devtools)))
suppressWarnings(suppressMessages(library(tidyr)))
suppressWarnings(suppressMessages(library(ez)))
suppressWarnings(suppressMessages(library(lsr)))
suppressWarnings(suppressMessages(library(lmerTest)))
suppressWarnings(suppressMessages(library(papaja)))
suppressWarnings(suppressMessages(library(MOTE)))

```

# Introduction

The lifetime prevalence of major depressive disorder (MDD) is the highest among all mental disorders, with a rate of 18.7% in the Dutch population (de Graaf et al., 2012). A range of different treatment options are available, with pharmacotherapy and cognitive behavioral therapy being the most frequently applied forms of treatment (Nemeroff et al., 2003). Unfortunately, a considerable amount of patients does not benefit from these treatments or suffer from recurrent episodes after a completed therapy (Keller, 1994). Ultimately, after several recurrent depressive episodes, patients can be offered electroconvulsive therapy (ECT), a form of treatment that is accompanied by severe side effects such as anterograde and retrograde memory impairments (for a review see Ingram, Saling, & Schweitzer, 2008). Less invasive forms of therapy are urgently required for otherwise treatment-resistant patients (Keller, 1994). 



# Methods






## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
